---
title: "Line item levels and simple differences"
output: html_document

params:
  program_path:     "[path]"
  date_max:         "20250118"
  year_lag:         2
  label_size:       11 # size of chart legend, axis labels
  title_size:       14 # size of chart titles
  data:             "monthly_sa" # vals df; intermediate feather file in "data/"
  meta:             "h8_meta" # meta df; intermediate feather file in "data/"

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

# Setup -----------------------------------------------------------------

library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(data.table)
library(dtplyr)
library(feather)

options(scipen = 999)

# Format chart dates
date_end <- as.Date(params$date_max, format = "%Y%m%d")
date_start <- date_end - lubridate::years(params$year_lag)

# Load data and meta  ----------------------------------------------------

# Functions
program_list <- list.files(paste0(params$program_path, "R/"), full.names = T)
sapply(program_list, source)

data <- feather::read_feather(paste0(params$program_path,
                                     "/data/", params$data, ".feather")) %>%
  pivot_wider(names_from = series_id, values_from = value)

meta <- feather::read_feather(paste0(params$program_path,
                                     "/data/", params$meta, ".feather"))

# Ref and updated dates
as_of_date <- data %>%
  summarise(max = max(date)) %>%
  pull() %>%
  format("%B %d, %Y")

timestamp <- format(Sys.time(), "%B %d, %Y, %X")

last_updated <- file.mtime(paste0(params$program_path,
                                  "/data/", params$data, ".feather")) %>%
  format("%B %d, %Y")

```

Charts created using seasonally adjusted monthly levels data.  
Change defined as current month less prior month.  

**Run at: `r timestamp`**.  
Data last retrieved: `r last_updated`.  
Final observation on: `r as_of_date`.  

Source: [Board of Governors of the Federal Reserve System](https://www.federalreserve.gov/releases/h8/current/default.htm).  
Data release: [H.8 Assets and Liabilities of Commercial Banks in the United States](https://www.federalreserve.gov/datadownload/Choose.aspx?rel=H8). 

Disclosures: Repo contents do not necessarily reflect the views of the Board of Governors of the Federal Reserve System 
or any other current or prior employer. All views & errors my own.  

## Charts

### Commercial and Industrial Loans

```{r ci_chg, fig.width = 8, fig.height = 4.5, dev = 'svg', echo = FALSE}
format_df(data,
         line_item = "1023",
         meta_df = meta) %>%
  plot_stacked_bar(date_start = date_start,
                   date_end = date_end,
                   level_or_change = "change",
                   domestic = FALSE,
                   weekly = FALSE)
```

```{r ci_levels, fig.width = 8, fig.height = 4.5, dev = 'svg', echo = FALSE}
format_df(data,
         line_item = "1023",
         meta_df = meta) %>%
  plot_stacked_bar(date_start = date_start,
                   date_end = date_end,
                   level_or_change = "levels",
                   domestic = FALSE,
                   weekly = FALSE)
```