---
title: "Line item levels and simple differences"
output:
  html_document: default
  pdf_document: default
params:
  program_path: "[path]"
  date_max:     "20250101"
  year_lag:     2
  label_size:   11 # size of chart legend, axis labels
  title_size:   14 # size of chart title
  data:         "monthly_sa" # vals df; intermediate feather file in "data/"
  meta:         "h8_meta" # meta df; intermediate feather file in "data/"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

# Setup -----------------------------------------------------------------

library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(data.table)
library(dtplyr)
library(feather)

options(scipen = 999)

# Format chart dates
date_end <- as.Date(params$date_max, format = "%Y%m%d")
date_start <- date_end - lubridate::years(params$year_lag)

# Load data and meta  ----------------------------------------------------

# Functions
program_list <- list.files(paste0(params$program_path, "R/"), full.names = T)
sapply(program_list, source)

data <- feather::read_feather(paste0(params$program_path,
                                     "/data/", params$data, ".feather")) %>%
  pivot_wider(names_from = series_id, values_from = value)

meta <- feather::read_feather(paste0(params$program_path,
                                     "/data/", params$meta, ".feather"))

# Ref and updated dates
as_of_date <- data %>%
  summarise(max = max(date)) %>%
  pull() %>%
  format("%B %d, %Y")

timestamp <- format(Sys.time(), "%B %d, %Y, %X")

last_updated <- file.mtime(paste0(params$program_path,
                                  "/data/", params$data, ".feather")) %>%
  format("%B %d, %Y")

output_plots <- function(line_id) {

  level <- format_df(data,
                     line_item = line_id,
                     meta_df = meta) %>%
              plot_stacked_bar(date_start = date_start,
                               date_end = date_end,
                               level_or_change = "levels",
                               domestic = FALSE,
                               weekly = FALSE)

  print(level)

  chg <- format_df(data,
                 line_item = line_id,
                 meta_df = meta) %>%
          plot_stacked_bar(date_start = date_start,
                           date_end = date_end,
                           level_or_change = "change",
                           domestic = FALSE,
                           weekly = FALSE)

  print(chg)

}

lines_to_chart <- c(
      "1001"
    , "1002", "1003", "1301", "1302", "1011", "1303", "1304"
    , "1020"
    , "1023"
    , "1026", "1221", "1027", "1220", "3219", "1215", "1216", "1217", "1218"
    , "1029", "1247", "3248", "1243", "2245"
    , "3305", "1030", "2310"
    , "1043"
    , "1048", "3092", "1047", "3053"
    , "1151"
    , "1058", "1072", "1110"
    , "3094", "1100", "3095"
    , "1152"
)

```

Charts created using seasonally adjusted monthly levels data.  
Change defined as current month less prior month.  

**Run at: `r timestamp`**.  
Data last retrieved: `r last_updated`.  
Final observation on: `r as_of_date`.  

Source: [Board of Governors of the Federal Reserve System](https://www.federalreserve.gov/releases/h8/current/default.htm).  
Data release: [H.8 Assets and Liabilities of Commercial Banks in the United States](https://www.federalreserve.gov/datadownload/Choose.aspx?rel=H8). 

Disclaimers: Contents do not necessarily reflect the views of the Board of Governors of the Federal Reserve System 
or any other current or prior employer. All views & errors my own.  



## Balance sheet line items

```{r, results = 'asis', echo = FALSE}
for (i in seq_along(lines_to_chart)) {

  cat("\n")
  cat("### ", unique(meta[meta$item == lines_to_chart[i], ]$short_desc), "\n")
  output_plots(lines_to_chart[i])
  cat("\n")
  cat("\n")

}

```

